\newcommand{\firstFormula}{

\begin{equation}
    f_N(t) = \begin{bmatrix}
        x_N(t) \\ y_N(t)
    \end{bmatrix} =
    \begin{cases}
        \begin{bmatrix}
            t - \dfrac{f'(x_o)}{|f`(x_o)|} N cos (tan^{-1} \left( -\dfrac{1}{f'(x_o)} \right) ) \\
            f(t) - - \dfrac{f'(x_o)}{|f`(x_o)|} N sin (tan^{-1} \left( -\dfrac{1}{f'(x_o)} \right) )
        \end{bmatrix}, & t \ni f'(t) \neq 0 \\
        \begin{bmatrix}
            t \\ f(t) + N
        \end{bmatrix}, & t \ni f'(t) = 0
    \end{cases}
\end{equation}

}

\section{A First Formula}

Let $f: \mathbb{R} \to \mathbb{R}$ be any arbitrary twice differentiable function whose second derivative $f''$
is continuous. These are the kinds of functions this paper we’ll use to establish the science of the N-Units Away Curves. While you can talk about the building of an N-Units Away Curve from a segment of a function (not on all of $\mathbb{R}$), it’s very similar and just not as interesting. Likewise you can also talk about making N-Units Away Curves for functions that are non-differentiable or discontinuous, but in that case things often get very nasty very quickly.

Take your function $y=f(x)$ and we’re now going to re-express that same function as a parametric function in terms of a variable $t$: 
$
\begin{bmatrix}
    x(t) \\ y(t)
\end{bmatrix}
= 
\begin{bmatrix}
    t \\ f(t)
\end{bmatrix}
$
, where $t$ assumes all values $t \in (- \infty, \infty)$. Pick any value $t_o \in \mathbb{R}$. $t_o$ corresponds to one unique point on the original curve $y=f(x)$, specifically the point $(t_o , f(t_o ))$. Fix an $N \in \mathbb{R}$. To every one of these points we are going to construct an associated point that lies exactly $N$ units away in the direction of the normal line to the curve at that point. Let $x_o = t_o$ . It’s a basic Calc 1 fact that at $x = x_o$ , the slope of the normal line is $-\dfrac{1}{f'(x_o)}$, assuming $f'(x_o)$ is non-zero. We can use arctangent to convert from slope to degrees. We get that the angle from the positive $x$-axis to the normal line is $tan^{-1} \left( -\dfrac{1}{f'(x_o)} \right) $. We can then use $cos(\theta)$ to convert this angle to an $x$-distance and $sin(\theta)$ to convert this angle to a $y$-distance. If we multiply these both by $N$ we can obtain a normal vector $\langle N cos (tan^{-1} \left( -\dfrac{1}{f'(x_o)} \right) ), N sin ( tan^{-1} \left( -\dfrac{1}{f'(x_o)} \right) ) \rangle $ which is exactly $N$ units long and points in the direction of the normal line to the curve $y = f(x)$ at $x = x_o$. The only last issue that causes trouble is the issue of which way we are trying to travel on that normal line? Let’s define it such that when N is positive, we obtain points $N$ units away and above the curve $y = f(x)$, and when $N$ is negative, we obtain points $N$ units away and below the curve. When $f'(x_o)$ is negative, the normal vector stated above points up and to the right, so we’re fine. It points to a spot above the curve. When $f'(x_o)$ is positive however, the normal vector points down and to the right, so we must multiply the whole vector by $-1$. This resolves the issue. We arrive at the desired normal vector that points $N$ units away into the ``up'' direction along the normal line to $y = f(x)$ at $x = x_o$. That vector is $\langle - \dfrac{f'(x_o)}{|f`(x_o)|} N cos (tan^{-1} \left( -\dfrac{1}{f'(x_o)} \right) ), - \dfrac{f'(x_o)}{|f`(x_o)|} N sin (tan^{-1} \left( -\dfrac{1}{f'(x_o)} \right) ) \rangle$.

We can utilize this to derive a parametric formula for the $N$-Units Away Curve to $y=f(x)$
in all cases where $f'(x_o) \neq 0$. But what about when is equal to 0? It’s nice and simple then.
We simply move $N$ units along a perfectly vertical normal line.

Thus the formula for the $N$-Units Away Curve to $y=f(x)$ is:

\firstFormula
